---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# KINNET

<!-- badges: start -->
<!-- badges: end -->

This package provides the functionality to process PamGene's PamChip
    Data Output and generate kinase interaction networks from that.

This project uses a bayesian algorithm to generate bayesian networks for
     defining dependence relationships between peptide sequences in the PamChip data.
     It then uses a novel kinase assignment method to assign upstream kinases to each 
     peptide which is then output as a graph.

## Installation

You can install the released version of KINNET from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("KINNET")
```

You can install the latest development version of KINNET from [Github]() with:

``` r
remotes::install_github("AliSajid/KINNET")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(KINNET)
## basic example code
```
